\subsection{External Interface Requirements}

\subsubsection{User Interfaces}

\subsubsection{Hardware Interfaces}
The CodeKataBattle platform operates entirely through web interfaces, eliminating the need for specialized hardware interfaces. Users can access the platform using standard web-enabled devices, such as computers, tablets, and smartphones. The platform is designed to function within a web browser, requiring no specific hardware beyond a device capable of running a modern browser and accessing the internet. This approach ensures broad accessibility without necessitating particular hardware configurations, making the platform versatile and user-friendly across various hardware setups. However, for optimal experience, at least 2GB of RAM and a minimum of 1GB of free space are recommended for browser caching and temporary files.

\subsubsection{Software Interfaces}
Our platform CKB interfaces with various software systems:

\begin{itemize}
    \item \textbf{Web Browsers:} Platform operates on web browsers. For universal access and easy use, it is compatible with major browsers like Chrome, Edge, Safari, Opera, and Firefox.

    \item \textbf{GitHub API:} Integrated for creating coding repositories and managing code \textit{submission} processes.

    \item \textbf{Sandboxing:} To create an isolated testing environment, our Sandbox Manager will utilise Docker.

    \item \textbf{Static Analysis Tool:} SonarQube API will be integrated for scoring the quality aspect of the code with static analysis. 

    \item \textbf{Database Technology:} Platform uses databases such as PostgreSQL.

    \item \textbf{Hosting:} Our platform uses Amazon Web Services EC2 for web server and database hosting.

    \item \textbf{Cloud File Storage:} The files will be stored using Amazon S3 services.

    \item \textbf{Email Service:} Amazon Simple Email Service SES will be used to send automated email notifications.
\end{itemize}

\subsubsection{Communication Interfaces}
Our platform utilises various communication systems:

\begin{itemize}
    \item \textbf{HTTPS:} For secure connection over the internet.

    \item \textbf{RESTful APIs:} We have RESTful APIs to communicate with the requests coming from GitHub Actions and the web application.

    \item \textbf{SMTP:} It is used to manage to send automated emails.
\end{itemize}

\subsection{Functional Requirements}

